The Unicode Cookbook \linebreak for Linguists

### 2015-12-10 book/chapters/ipa_background.tex
typo

Established in 1886, the \textsc{international phonetic association} (henceforth
\textit{Association}) has long maintained a standard alphabet, the
\texsct{international phonetic alphabet} (henceforth \textit{IPA}), which is a
common standard in linguistics to transcribe sounds of spoken languages. It was
first published in 1888 as an international system of phonetic transcription for
oral languages and for pedagogical purposes. It contained phonetic values for
English, French and German. Diacritics for length and nasalization were already
present in this first version, and the same symbols are still used today. 
%\footnote{Also referred to as API, for \textit{Association Phonétique Internationale}.}

@@

	\item it is intended to be a set of symbols for representing all possible
       sounds in the world's (spoken) languages;
	\item its chart has a linguistic basis (specifically a phonological bias)
       rather than a general phonetic notation scheme;
	\item its symbols can be used to represent distinctive feature
       combinations;\footnote{Although the chart uses traditional manner and
       place of articulation labels, the symbols can be used as a representation
       of any defined bundle of features, binary or otherwise, to define
       phonetic dimensions.}
	\item its chart provides a summary of linguists' agreed-upon phonetic 
	knowledge.

>>>>

Established in 1886, the \textsc{international phonetic association} (henceforth
\textit{Association}) has long maintained a standard alphabet, the
\texsc{international phonetic alphabet} (henceforth \textit{IPA}), which is a
common standard in linguistics to transcribe sounds of spoken languages. It was
first published in 1888 as an international system of phonetic transcription for
oral languages and for pedagogical purposes. It contained phonetic values for
English, French and German. Diacritics for length and nasalization were already
present in this first version, and the same symbols are still used today. 
%\footnote{Also referred to as API, for \textit{Association Phonétique Internationale}.}

@@

	\item it is intended to be a set of symbols for representing all possible
       sounds in the world's (spoken) languages;
	\item its chart has a linguistic basis (specifically a phonological bias)
       rather than just being a general phonetic notation scheme;
	\item its symbols can be used to represent distinctive feature
       combinations;\footnote{Although the chart uses traditional manner and
       place of articulation labels, the symbols can be used as a representation
       of any defined bundle of features, binary or otherwise, to define
       phonetic dimensions.}
	\item its chart provides a summary of linguists' agreed-upon phonetic 
	knowledge.
